The relative roles of genetic, ecological and environmental factors in species radiations

### 2018-02-20 paper/draft.tex
comment
extend M&M

@@

\section{Discussion}
Shortcomings. (/Processes/Factors not considered.)
(Dynamic) resource availability: assumed constant in model, but petentially more variation, complexity in community dynamics.
Interaction: in present model only indirect interaction via competition, but predation, parasitation, herbivory, mutualism will increase complexity.
Especially pollination is assumed to be an important interaction, because having a high impact on evolution and establishment of species due to specialization.
[maybe some words on trophic interactions.]

>>>>

Building on the model of Cabral et al. (2017a, b), most of the biological rates are controlled following the metabolic theory
of ecology (MTE, Brown et al.\ 2004).
In MTE, a biological rate $b$ depends on the temperature $T$ and individual mass $M$, scaling a base rate $b_0$ as:
\begin{equation}
  $b=b_0*M^{3/4}*exp(-E_A/{k_B*T})$
  \label{eq:MTE}
\end{equation}
with $E_A$ the activation energy and $k_B$ the Boltzman constant.

@@

\section{Discussion}
Shortcomings. (/Processes/Factors not considered.)
(Dynamic) resource availability: assumed constant in model, but petentially more variation, complexity in community dynamics.
Interaction: in present model only indirect interaction via competition, but predation, parasitation, herbivory, mutualism will increase complexity.
Especially pollination is assumed to be an important interaction, because having a high impact on evolution and establishment of species due to specialization.
%[maybe some words on trophic interactions.]
